---
title: "Biden Transition Analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: cerulean
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(lubridate)
library(janitor)
library(scales)
library(gt)
library(kableExtra)
library(glue)
library(plotly)
library(DT)
library(htmlwidgets)
library(htmltools)
options(dplyr.summarise.inform = FALSE)

#run the script for step 03 to update the datasets to caputre the current live verions
#and load all the new dataset objects into the environment (you'll see them populate on the upper right window)
source("03_compare_current_with_previous_BrittneyHo.R")
```

White House Staff
==================================
Here are the White House Senior Staff members that have been named to the Biden Administration. To sort, use the up/down arrows by the column names. 

Row {data-width=1000}
-----------------------------------------------------------------------

### White House Staff (as of Dec. 16, 2020)

```{r}

staff_data_current_filtered <- staff_data_current %>%
  select(
    name, title, -link, -idstring
  ) %>%
  rename(
    Name = name,
    Title = title
  )

datatable(staff_data_current_filtered,
          filter = "top",
          extensions = "Buttons",
          options = list(searchHighlight = TRUE, bPaginate = FALSE, dom = 'Bfrtip', 
        buttons = c('copy', 'csv', 'excel', 'print')
          )) 

```

Agency Review Team
==================================
Here are the appointees to the Agency Review Teams that have been named to the Biden Administration. To sort, use the up/down arrows by the column names. To filter, click on the boxes at the top of the columns. 

Row {data-width=1000}
-----------------------------------------------------------------------

### Agency Review Team (as of Dec. 16, 2020)

```{r}
transition_data_current_filtered <- transition_data_current %>%
  select(
    agency, name, team_lead, on_multiple_teams, most_recent_employment, source_of_funding, -idstring, -namestring
    ) %>%
  mutate(
    team_lead = as.factor(team_lead),
    on_multiple_teams = as.factor(on_multiple_teams),
    source_of_funding = as.factor(source_of_funding)
  ) %>%
  rename(
    Agency = agency,
    Name = name,
    "Team Lead" = team_lead,
    "On Multiple Teams" = on_multiple_teams,
    "Most Recent Employment" = most_recent_employment,
    "Source of Funding" = source_of_funding
  ) 
 
datatable(transition_data_current_filtered,
          filter = "top",
          extensions = "Buttons",
          options = list(searchHighlight = TRUE, bPaginate = FALSE, dom = 'Bfrtip', 
        buttons = c('copy', 'csv', 'excel', 'print')
          )) 
```

Agency Review Team Growth from November to December
==================================
Let's take a look at some the growth that each agency review team faced in the weeks following Biden's election. Examining data from November 24, 2020 to December 16, 2020, just shy of a month, we can see the percent change in each agency, perhaps reflective of areas of prioritized importance to the president-elect.

Row {data-width=1000}
-----------------------------------------------------------------------
### Agency Review Team Growth from Nov. to Dec.

```{r}

agencycount_comparefiltered <- agencycount_compare %>%
  mutate(pct_change = ((current_count - previous_count)/previous_count)) %>%
  rename(
    Agency = agency,
    "Count as of Dec. 16" = current_count,
    "Count as of Nov. 24" = previous_count,
    "Change" = change,
    "Percent Change" = pct_change 
  )
  

datatable(agencycount_comparefiltered) 
  

```
